Measurement and Probability in Fuzzy Quantum Theories

### 2017-03-05 prop_iop.tex
prop_iop.tex \section{Mermin Square} Updating...

The Kochen-Specker theorem asserts that there is no function~$v$
assigning a definitely value to all observables such that
\begin{equation}\eqalign{ 
v\left(O_{1}\right)+v\left(O_{2}\right)=v\left(O_{1}+O_{2}\right)\textrm{ and}\\
v\left(O_{1}\right)v\left(O_{2}\right)=v\left(O_{1}O_{2}\right)
}\label{eq:Kochen-Specker-Rules}\end{equation}
if $O_{1}$ and $O_{2}$ are commuting observables. Based on these
two properties, they first proved that $v$ must send an observable
to its eigenvalues so that the following observables~\cite{Mermin1990Simple,peres1995quantum}:
\begin{equation}
\begin{array}{ccc}
\mathbb{1}\otimes\sigma_{z} & \sigma_{z}\otimes\mathbb{1} & \sigma_{z}\otimes\sigma_{z}\\
\sigma_{x}\otimes\mathbb{1} & \mathbb{1}\otimes\sigma_{x} & \sigma_{x}\otimes\sigma_{x}\\
\sigma_{x}\otimes\sigma_{z} & \sigma_{z}\otimes\sigma_{x} & \sigma_{y}\otimes\sigma_{y}
\end{array}\label{eq:MerminSquare}
\end{equation}
must be sent to $1$ or $-1$. In each row and column, operators commutes,
and each operator is the product of the two others, except in the
third column $\left(\sigma_{z}\otimes\sigma_{z}\right)\left(\sigma_{x}\otimes\sigma_{x}\right)=-\sigma_{y}\otimes\sigma_{y}$.
Therefore, it is clear impossible to find a function~$v$ such that
\begin{equation}
\begin{array}{ccc}
v\left(\mathbb{1}\otimes\sigma_{z}\right) & v\left(\sigma_{z}\otimes\mathbb{1}\right) & v\left(\sigma_{z}\otimes\sigma_{z}\right)\\
v\left(\sigma_{x}\otimes\mathbb{1}\right) & v\left(\mathbb{1}\otimes\sigma_{x}\right) & v\left(\sigma_{x}\otimes\sigma_{x}\right)\\
v\left(\sigma_{x}\otimes\sigma_{z}\right) & v\left(\sigma_{z}\otimes\sigma_{x}\right) & v\left(\sigma_{y}\otimes\sigma_{y}\right)
\end{array}\label{eq:MerminSquare-values}
\end{equation}
satisfying equation~(\ref{eq:Kochen-Specker-Rules}).

>>>>

The Kochen-Specker theorem asserts that there is no function~$v$
assigning a definitely value to all observables such that
\begin{equation}\eqalign{ 
v\left(O_{1}\right)+v\left(O_{2}\right)=v\left(O_{1}+O_{2}\right)\textrm{ and}\\
v\left(O_{1}\right)v\left(O_{2}\right)=v\left(O_{1}O_{2}\right)
}\label{eq:Kochen-Specker-Rules}\end{equation}
if $O_{1}$ and $O_{2}$ are commuting observables. Suppose that there
is a function~$v$ satisfying these two properties, it must send
an observable to its eigenvalues so that the following observables~\cite{Mermin1990Simple,peres1995quantum}:
\begin{equation}
\begin{array}{ccc}
\mathbb{1}\otimes\sigma_{z} & \sigma_{z}\otimes\mathbb{1} & \sigma_{z}\otimes\sigma_{z}\\
\sigma_{x}\otimes\mathbb{1} & \mathbb{1}\otimes\sigma_{x} & \sigma_{x}\otimes\sigma_{x}\\
\sigma_{x}\otimes\sigma_{z} & \sigma_{z}\otimes\sigma_{x} & \sigma_{y}\otimes\sigma_{y}
\end{array}\label{eq:MerminSquare}
\end{equation}
must be sent to $1$ or $-1$. In each row and column, operators commutes,
and each operator is the product of the two others, except in the
third column $\left(\sigma_{z}\otimes\sigma_{z}\right)\left(\sigma_{x}\otimes\sigma_{x}\right)=-\sigma_{y}\otimes\sigma_{y}$.
Therefore, it is clear impossible to find a function~$v$ such that
\begin{equation}
\begin{array}{ccc}
v\left(\mathbb{1}\otimes\sigma_{z}\right) & v\left(\sigma_{z}\otimes\mathbb{1}\right) & v\left(\sigma_{z}\otimes\sigma_{z}\right)\\
v\left(\sigma_{x}\otimes\mathbb{1}\right) & v\left(\mathbb{1}\otimes\sigma_{x}\right) & v\left(\sigma_{x}\otimes\sigma_{x}\right)\\
v\left(\sigma_{x}\otimes\sigma_{z}\right) & v\left(\sigma_{z}\otimes\sigma_{x}\right) & v\left(\sigma_{y}\otimes\sigma_{y}\right)
\end{array}\label{eq:MerminSquare-values}
\end{equation}
satisfying equation~(\ref{eq:Kochen-Specker-Rules}).
